Powdery mildew yield loss mitigation strategies in mungbean, a meta-analysis.

### 2020-01-23 DataWrangle/ExcludeBook_191115_PMMB_DataWrangling_PM.Rmd
Wrangled the AUDPC into the data

head(Fogerty_17)
unique(Fogerty_17$Chem.Trt)
unique(Fogerty_17$Chemical)
Fogerty_17[,7:11]
```

@@

@@

@@

# Start from here

@@

#dim(Well_18)   # 72 rows , 32 Columns
#names(Well_18)

# Columns to keep
Well_18 <- Well_18[, c('Plot','Rep','Plant.Pop','Row.Spacing',
            'Fungicide','Treatment','IR.23-3-18',
            'IR.5-4-18','IR.11-4-18','IR.18-4-18',
            'IR.26-4-18','IR.2-5-18','S.23-3-18',
            'S.5-4-18','S.11-4-18','S.18-4-18',
            'S.26-4-18','S.2-5-18','Row.Length','Yield./.ha')]

Well_18_means <- Well_18 %>%
   group_by(Row.Spacing, Fungicide, Plant.Pop) %>%
   summarise(
      Yield = mean(`Yield./.ha`, na.rm = TRUE),
      Incidence  = max(Well_18.1$Incidence),
      Severity  = max(Severity, na.rm = TRUE)
   )

# respectively
# plot and treatment variables
# Incidence assessment
# severity assessment
# Yield assessment

Well_18_inc <-
   reshape(
      data = Well_18,
      idvar = "Plot",
      direction = "long",
      varying = list(incidence = names(Well_18)[7:12]),
      timevar = "ass_date_i"
   )

Well_18_sev <-
   reshape(
      data = Well_18,
      idvar = "Plot",
      direction = "long",
      varying = list(incidence = names(Well_18)[13:18]),
      timevar = "ass_date_s"
   )

Well_18.1 <- cbind(Well_18_inc[, c(1:6, 13:16)], Well_18_sev[, 15:16])

names(Well_18.1)[10] <- c("Incidence")
names(Well_18.1)[12] <- c("Severity")
Well_18.1$ass_date_i <- rep(names(Well_18_inc)[7:12], each = 72)
Well_18.1$ass_date_i <-
   as.Date(gsub("S.", "", Well_18.1$ass_date_i), format = "%d-%m-%y")
names(Well_18.1)[9] <- c("Assessment_date")
Well_18.1 <- Well_18.1[c(1:10, 12)]

Well_18.1$Row.Spacing <-
   as.numeric(unlist(strsplit(Well_18.1$Row.Spacing, " mtr")))

write.csv(
   Well_18.1,
   "C:/Users/U8011054/OneDrive - USQ/Cloudstor/Mungbean/2018_Wellcamp.csv"
)

Well_18$FungVCon <- Well_18$Fung.Trt
Well_18[Well_18$FungVCon == 1,"FungVCon"] <- 3
Well_18[Well_18$FungVCon == 4,"FungVCon"] <- 1
Well_18[Well_18$FungVCon == 3,"FungVCon"] <- 2

Well_18_means <- Well_18.1 %>%
   group_by(Row.Spacing, Fungicide, Plant.Pop) %>%
   summarise(
      Yield = mean(`Yield./.ha`, na.rm = TRUE),
      Incidence  = max(Well_18.1$Incidence),
      Severity  = max(Severity, na.rm = TRUE),
      meanSq = anova(lm(`Yield./.ha` ~ factor(Plant.Pop) + factor(FungVCon) + `Row.Spacing`, data = subset(Well_18, Fungicide != "Custodia")))[2,3] # of only triazoles
   )

@@

### Hermitage 2019
```{r Herm19}
PM_MB_19 <-
   read.xlsx(
      "C:/Users/U8011054/USQ/SCP - Documents/DAW1810/mungbean_powdery-mildew/1901_Herm_PM/1901 Mungbean powdery mildew disease and yeild data.xlsx",
      startRow = 2,
      cols = c(1:21)
   )

# Remove these plots as the results can't be trusted
PM_MB_19 <- subset(PM_MB_19, Harvest.Plot.Number != 5)
PM_MB_19 <- subset(PM_MB_19, Harvest.Plot.Number != 6)

PM_MB_19$AUDPC <- apply(PM_MB_19[,c("15-4-19.Incedence", "23-4-19.Incedence", "1-5-19.Incedence")]-1,1,FUN = audpc, dates = c(3,8,21))

PM_MB_19$Yeild

PM19_means <- PM_MB_19 %>%
   group_by(TOS.NUM, `T/ment.NUM`) %>%
   summarise(
      Incidence190423 = mean(`23-4-19.Incedence`, na.rm = TRUE),
      Inc.sd.190423 = sd(`23-4-19.Incedence`, na.rm = TRUE),
      Inc.error.190423 = "Stdev",
      Incidence190501 = mean(`1-5-19.Incedence`, na.rm = TRUE),
      Inc.sd.190501 = sd(`1-5-19.Incedence`, na.rm = TRUE),
      Inc.error.190501 = "Stdev",
      Plot_length = mean(Plot.Lengths, na.rm = TRUE),
      Yield = mean(Yeild/1000, na.rm = TRUE),
      Yield_error = sd(Yeild/1000, na.rm = TRUE),
      AUDPC = mean(AUDPC, na.rm = TRUE),
      meanSq = anova(lm(Yeild/1000 ~ factor(TOS.NUM) + factor(`T/ment.NUM`), data = PM_MB_19))[2,3]
   )

library(agricolae)

>>>>

@@

Fogerty_17_m <- fold_data(Fogerty_17_m, PM_MB_means)

@@

Herm_17_m <- fold_data(Herm_17_m, PM_MB_means)

@@

@@

colnames(Well_18)[13:14] <- c("Row.Spacing_ID", "Fungicide_ID")

@@

#### Define treatment data
```{r Well_18_treatmentDefine}
Well_18_dat <- Well_18 %>%
   mutate(trade_name = 
             case_when(Fung.Trt == 1 ~ "Folicur",
                       Fung.Trt == 3 ~ "Throttle",
                       Fung.Trt == 2 ~ "Custodia",
                       Fung.Trt == 4 ~ "control",
                       TRUE ~ "other"))%>%
   mutate(fungicide_ai = 
             case_when(Fung.Trt == 1 ~ "tebuconazole",
                       Fung.Trt == 3 ~ "propiconazole",
                       Fung.Trt == 2 ~ "200 g/L tebuconazole + 120 g/L azoxystrobin",
                       Fung.Trt == 4 ~ "control",
                       TRUE ~ "other"))%>%
   mutate(dose_ai.ha = 
             case_when(Fung.Trt == 1 ~ 60,
                       Fung.Trt == 2 ~ 62,
                       Fung.Trt == 3 ~ 125,
                       Fung.Trt == 4 ~ NA_real_,
                       TRUE ~ 9999))%>%
   mutate(Row.Spacing = 
             case_when(Row.Sp.Trt == 1 ~ 0.25,
                       Row.Sp.Trt == 2 ~ 0.5,
                       Row.Sp.Trt == 3 ~ 1,
                       TRUE ~ 9999))%>%
   mutate(fungicide_application_2 = 
             case_when(Fung.Trt <= 3 ~ as.Date("2018-04-16", format = "%Y-%m-%d"),
                       TRUE ~ as.Date(NA)))%>%
   mutate(fungicide_application_1 = 
             case_when(Fung.Trt == 4 ~ as.Date(NA),
                       Fung.Trt == 1 ~ as.Date("2018-03-28", format = "%Y-%m-%d"),
                       Fung.Trt == 2 ~ as.Date("2018-03-28", format = "%Y-%m-%d"),
                       Fung.Trt == 3 ~ as.Date("2018-03-28", format = "%Y-%m-%d"),
                       TRUE ~ as.Date(NA)))%>%
   mutate(spray_n = 
             case_when(Fung.Trt <= 3 ~ 2,
                       TRUE ~ NA_real_))

#### Input trial data
```{r Well18_Trialdat}

Well_18_dat <- 
   data.frame(trial_ref = "mung1718/01",
              year = "2018",
              location = "Wellcamp",
              host_genotype = "Jade",
              trial_design = "RCB",
              plot_length = Well_18_dat$Row.Length,
              plot_width = 2,
              plant_density = Well_18_dat$Plant.Pop,
              row_spacing = Well_18_dat$Row.Spacing,
              replicate = Well_18_dat$Rep,
              planting_date = as.Date("2018-02-13", format = "%Y-%m-%d"),
              emergence_date = as.Date(NA),
              flowering_date = as.Date(NA),
              pod_fill_date = as.Date(NA),
              mid_late_pod_fill = as.Date(NA),
              first_sign_disease = as.Date("2018-03-21", format = "%Y-%m-%d"),
              trade_name = as.factor(Well_18_dat$trade_name),
              fungicide_ai = Well_18_dat$fungicide_ai,
              dose_ai.ha = Well_18_dat$dose_ai.ha,
              n_treatment = Well_18_dat$Treatment,
              fungicide_application_1 = Well_18_dat$fungicide_application_1,
              fungicide_application_2 = Well_18_dat$fungicide_application_2,
              total_fungicide = Well_18_dat$spray_n,
              harvest_date = as.Date("2018-05-31", format = "%Y-%m-%d"),
              final_assessment = as.Date("2018-05-02", format = "%Y-%m-%d"),
              PM_final_severity = Well_18_dat$`IR.2-5-18`,
              rating_scale = "1-9",
              grain_yield.t.ha. = as.numeric(Well_18_dat$`Yield./.ha`)
               # -1 to the data because zero disease = 1 on rating scale// Dates are based off days from first sign
              )

Well_18_dat <- cbind(Well_18_dat,
                          AUDPC = apply(data.frame(zero = 1,
                                                   Well_18[,c("IR.23-3-18","IR.5-4-18", "IR.11-4-18", "IR.18-4-18","IR.26-4-18","IR.2-5-18")]-1),
                                        1, 
                                        FUN = audpc, 
                                        dates = c((Well_18_dat$first_sign_disease[1]-7)-
                                                     Well_18_dat$planting_date[1],
                                                  38,51 ,57,64,72,78)
                                        )
                          )

#### Calculating treatment means
```{r Well17_means}

Well_18_m <- Well_18_dat %>%
   group_by(host_genotype, n_treatment, row_spacing, fungicide_ai) %>%
   summarise(trial_ref = unique(trial_ref),
             year = unique(year),
             location = unique(location),
             trial_design = unique(trial_design),
             trade_name = unique(trade_name),
             dose_ai.ha = unique(dose_ai.ha),
             trial_ref = unique(trial_ref),
             plot_length.m. = mean(plot_length, na.rm = TRUE),
             plot_width.m. = mean(plot_width, na.rm = TRUE),
             plant_density = mean(plant_density, na.rm = TRUE),
             replicates = length(as.numeric(replicate)),
             planting_date = unique(planting_date),
             emergence_date = unique(emergence_date),
             flowering_date = unique(flowering_date),
             pod_fill_date = unique(pod_fill_date),
             mid_late_pod_fill = unique(mid_late_pod_fill),
             first_sign_disease = unique(first_sign_disease),
             fungicide_application_1 = unique(fungicide_application_1),
             fungicide_application_2 = unique(fungicide_application_2),
             total_fungicide = unique(total_fungicide),
             harvest_date = unique(harvest_date),
             final_assessment = unique(final_assessment),
             PM_final_severity = mean(PM_final_severity, na.rm = TRUE),
             rating_scale = unique(rating_scale),
             disease_error = sd(PM_final_severity, na.rm = TRUE), # why is this not working
             D_error_type = "stdev",
             grain_yield.t.ha. = mean(grain_yield.t.ha., na.rm = TRUE),
             raw_graded = NA,
             yield_error = sd(grain_yield.t.ha., na.rm = TRUE),
             Y_error_type = "stdev",
             AUDPC.m = mean(AUDPC),
             AUDPC.sd = sd(AUDPC),
             meanSq = anova(lm(grain_yield.t.ha. ~ 
                                  factor(n_treatment) + fungicide_ai + row_spacing, 
                               data = subset(Well_18_dat, trade_name != "Custodia")))[1,3] # of only triazoles
   )

# For some weird reason standard deviations are comming back NA in the code above
Well_18_m[,c("n_treatment","row_spacing", "disease_error","yield_error")] <- 
   Well_18_dat %>%
   group_by(n_treatment, row_spacing, fungicide_ai) %>%
   summarise(disease_error = sd(PM_final_severity, na.rm = TRUE),
             yield_error = sd(grain_yield.t.ha., na.rm = TRUE)) %>%
   select(c("disease_error","yield_error"))

Well_18_m <- fold_data(Well_18_m, PM_MB_means)

write.csv(
   Well_18_m,
   "C:/Users/U8011054/USQ/SCP - Documents/DAW1810/mungbean_powdery-mildew/Past trials/2018/Wellcamp/Wellcamp_18_mean.csv",
   row.names = FALSE
)

### Hermitage 2019
```{r Herm19}
PM_MB_19 <-
   read.xlsx(
      "C:/Users/U8011054/USQ/SCP - Documents/DAW1810/mungbean_powdery-mildew/1901_Herm_PM/1901 Mungbean powdery mildew disease and yeild data.xlsx",
      startRow = 2,
      cols = c(1:21)
   )
?audpc
# Remove these plots as the results can't be trusted
PM_MB_19 <- subset(PM_MB_19, Harvest.Plot.Number != 5)
PM_MB_19 <- subset(PM_MB_19, Harvest.Plot.Number != 6)

# Calculate area under the disease progress curve
PM_MB_19$AUDPC <- apply(data.frame(zero = 1,PM_MB_19[,c("15-4-19.Incedence", "23-4-19.Incedence", "1-5-19.Incedence")]-1),1,FUN = audpc, dates = c(60, 70,78,86))

# Calculate area under the disease progress curve for plots which were not assessed at on 2019-05-01
PM_MB_19[is.na(PM_MB_19$`1-5-19.Incedence`),"AUDPC"] <- 
   apply(data.frame(zero = 1,PM_MB_19[is.na(PM_MB_19$`1-5-19.Incedence`) ,c("15-4-19.Incedence", "23-4-19.Incedence")]-1),1,FUN = audpc, dates = c(60, 70,78))
```

#### Define treatment data
```{r Well_18_treatmentDefine}
Herm_19_dat <- PM_MB_19 %>%
   mutate(fungicide_application_1 = 
             case_when(`T/ment.NUM` == 1 ~ as.Date("2018-04-15", format = "%Y-%m-%d"),
                       `T/ment.NUM` == 2 ~ as.Date("2018-04-15", format = "%Y-%m-%d"),
                       `T/ment.NUM` == 3 ~ as.Date("2018-04-23", format = "%Y-%m-%d"),
                       `T/ment.NUM` == 4 ~ as.Date(NA),
                       TRUE ~ as.Date(NA)))%>%
   mutate(fungicide_application_2 = 
             case_when(`T/ment.NUM` == 2 ~ as.Date("2018-04-29", format = "%Y-%m-%d"),
                       TRUE ~ as.Date(NA)))%>%
   mutate(spray_n = 
             case_when(`T/ment.NUM` == 3 ~ 2,
                       `T/ment.NUM` <= 2 ~ 1,
                       TRUE ~ NA_real_))%>%
   mutate(trial_ref = 
             case_when(TOS.NUM == 1 ~ "mung1819/01",
                       TOS.NUM == 2 ~ "mung1819/02",
                       TRUE ~ NA_character_))%>%
   mutate(planting_date = 
             case_when(TOS.NUM == 1 ~ as.Date("2018-02-04", format = "%Y-%m-%d"),
                       TOS.NUM == 2 ~ as.Date("2018-02-18", format = "%Y-%m-%d"),
                       TRUE ~ as.Date(NA)))%>%
   mutate(emergence_date = 
             case_when(TOS.NUM == 1 ~ as.Date("2018-02-11", format = "%Y-%m-%d"),
                       TOS.NUM == 2 ~ as.Date("2018-02-25", format = "%Y-%m-%d"),
                       TRUE ~ as.Date(NA)))%>%
   mutate(final_assessment = 
             case_when(TOS.NUM == 1 ~ as.Date("2018-04-24", format = "%Y-%m-%d"),
                       TOS.NUM == 2 ~ as.Date("2018-05-01", format = "%Y-%m-%d"),
                       TRUE ~ as.Date(NA)))%>%
   mutate(PM_final_severity = 
             case_when(is.na(`1-5-19.Incedence`) ~ `23-4-19.Incedence`,
                       TRUE ~ `1-5-19.Incedence`))%>%
   mutate(trade_name = 
             case_when(`T/ment.NUM` == 4 ~ NA_character_,
                       TRUE ~ "Folicur"))%>%
   mutate(fungicide_ai = 
             case_when(`T/ment.NUM` == 4 ~ NA_character_,
                       TRUE ~ "tebuconazole"))%>%

   mutate(dose_ai.ha = 
             case_when(`T/ment.NUM` == 4 ~ NA_real_,
                       TRUE ~ 62))%>%
   mutate(meanSq = 
             case_when(TOS.NUM == 1 ~ anova(lm(Yeild/1000 ~ 
                                  factor(`T/ment.NUM`) , 
                               data = PM_MB_19[PM_MB_19$TOS.NUM == 1,]))[1,3],
                       TOS.NUM == 2 ~ anova(lm(Yeild/1000 ~ 
                                  factor(`T/ment.NUM`) , 
                               data = PM_MB_19[PM_MB_19$TOS.NUM == 2,]))[1,3],
                       TRUE ~ NA_real_))

#### Input trial data
```{r Well18_Trialdat}

Herm_19_dat <- 
   data.frame(trial_ref = Herm_19_dat$trial_ref,
              year = "2019",
              location = "Hermitage",
              host_genotype = "Jade",
              trial_design = "RCB",
              plot_length = Herm_19_dat$Plot.Lengths,
              plot_width = 2,
              plant_density = NA_character_,
              row_spacing = 0.25,
              replicate = Herm_19_dat$Rep.Num,
              planting_date = Herm_19_dat$planting_date,
              emergence_date = Herm_19_dat$emergence_date,
              flowering_date = as.Date(NA),
              pod_fill_date = as.Date(NA),
              mid_late_pod_fill = as.Date(NA),
              first_sign_disease = as.Date("2018-04-12", format = "%Y-%m-%d"),
              trade_name = as.factor(Herm_19_dat$trade_name),
              fungicide_ai = Herm_19_dat$fungicide_ai,
              dose_ai.ha = Herm_19_dat$dose_ai.ha,
              n_treatment = Herm_19_dat$`T/ment.NUM`,
              fungicide_application_1 = Herm_19_dat$fungicide_application_1,
              fungicide_application_2 = Herm_19_dat$fungicide_application_2,
              total_fungicide = Herm_19_dat$spray_n,
              harvest_date = as.Date("2018-05-22", format = "%Y-%m-%d"),
              final_assessment = Herm_19_dat$final_assessment,
              PM_final_severity = Herm_19_dat$PM_final_severity,
              rating_scale = "1-9",
              grain_yield.t.ha. = as.numeric(Herm_19_dat$Yeild)/1000,
              meanSq = Herm_19_dat$meanSq
              )

Herm_19_dat$plant_density

unique(Herm_19_dat$plot_length)
mean(Herm_19_dat$plant_density, na.rm = TRUE)

```{r Herm19_means}

Herm_19_m <- Herm_19_dat %>%
   group_by(trial_ref, n_treatment) %>%
   summarise(year = unique(year),
             location = unique(location),
             trial_design = unique(trial_design),
             trade_name = unique(trade_name),
             dose_ai.ha = unique(dose_ai.ha),
             plot_length.m. = mean(plot_length, na.rm = TRUE),
             plot_width.m. = mean(plot_width, na.rm = TRUE),
             plant_density = NA_character_,
             replicates = length(as.numeric(replicate)),
             planting_date = unique(planting_date),
             emergence_date = unique(emergence_date),
             flowering_date = unique(flowering_date),
             pod_fill_date = unique(pod_fill_date),
             mid_late_pod_fill = unique(mid_late_pod_fill),
             first_sign_disease = unique(first_sign_disease),
             fungicide_application_1 = unique(fungicide_application_1),
             fungicide_application_2 = unique(fungicide_application_2),
             total_fungicide = unique(total_fungicide),
             harvest_date = unique(harvest_date),
             final_assessment = unique(final_assessment),
             PM_final_severity = mean(PM_final_severity, na.rm = TRUE),
             rating_scale = unique(rating_scale),
             disease_error = sd(PM_final_severity, na.rm = TRUE), # why is this not working
             D_error_type = "stdev",
             grain_yield.t.ha. = mean(grain_yield.t.ha., na.rm = TRUE),
             raw_graded = NA,
             yield_error = sd(grain_yield.t.ha., na.rm = TRUE),
             Y_error_type = "stdev",
             AUDPC.m = mean(AUDPC),
             AUDPC.sd = sd(AUDPC),
             meanSq = unique(meanSq)
   )

# For some weird reason standard deviations are comming back NA in the code above
# Herm_17_m[,c("n_treatment","row_spacing", "disease_error","yield_error")] <- 
#    Herm_17_dat %>%
#    group_by(n_treatment, row_spacing, fungicide_ai) %>%
#    summarise(disease_error = sd(PM_final_severity, na.rm = TRUE),
#              yield_error = sd(grain_yield.t.ha., na.rm = TRUE)) %>%
#    select(c("disease_error","yield_error"))
#

Herm_19_m <- fold_data(Herm_19_m, PM_MB_means)

write.csv(
   Herm_17_m,
   "C:/Users/U8011054/USQ/SCP - Documents/DAW1810/mungbean_powdery-mildew/Past trials/2019/Hermitage/Hermitage_19_mean.csv",
   row.names = FALSE
)

```{r}
PM19_means <- PM_MB_19 %>%
   group_by(TOS.NUM, `T/ment.NUM`) %>%
   summarise(
      Incidence190423 = mean(`23-4-19.Incedence`, na.rm = TRUE),
      Inc.sd.190423 = sd(`23-4-19.Incedence`, na.rm = TRUE),
      Inc.error.190423 = "Stdev",
      Incidence190501 = mean(`1-5-19.Incedence`, na.rm = TRUE),
      Inc.sd.190501 = sd(`1-5-19.Incedence`, na.rm = TRUE),
      Inc.error.190501 = "Stdev",
      Plot_length = mean(Plot.Lengths, na.rm = TRUE),
      Yield = mean(Yeild/1000, na.rm = TRUE),
      Yield_error = sd(Yeild/1000, na.rm = TRUE),
      AUDPC = mean(AUDPC, na.rm = TRUE),
      meanSq = anova(lm(Yeild/1000 ~ factor(TOS.NUM) + factor(`T/ment.NUM`), data = PM_MB_19))[2,3]
   )
